---
title: "Wedding Invitations - Risk Modeling (Version 2.0)"
author: "Bryan Clark"
date: "20202-08-29"
output:
  html_document:
    highlight: default
    theme: cosmo
    toc: yes
    toc_float: yes
    df_print: kable
---

NOTES:
+ convert class into package
+ incorporate python code in R package
+ create unit tests

```{r setup, include = FALSE}
# customize output options 
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 6, fig.asp = 0.618, out.width = "70%", 
                      fig.align = "center")

# rmarkdown
library(knitr)
library(kableExtra)

# python
library(reticulate)
use_miniconda("wedding_risk", required = TRUE)
#reticulate::use_virtualenv(fs::path(here::here(), "venv"), required = T)
py_path <- fs::path(here::here(), "py", "simulator.py")
source_python(py_path)

# core
library(tidyverse)

# set theme for plots
theme_set(theme_minimal(base_family = "Avenir"))

# Color-blind palette with grey:
cb_palette <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
                "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# TL;DR

## Context

Last year I got a taste of the power of shiny. 
Just finished Shing with AWS course. 
Want to find a good way to apply learnings and continue progress of shiny app deployment. 

## Goals

+ Create shiny app project library to reinforce learnings from Shiny with AWS course
+ Practice setting up docker with R and Python
+ 

## Solution

+ Launch the start of Shiny Business Analytics with a remix of the Wedding Invitiation Risk Modeling App. 

# Monte Carlo Simulation

+ Describe benefits (mention Fooled By Randomness)
+ Outline three approaches to support (fixed, equal range, best/worst/most likely triangle) and reasoning
  + User reasons
  + Shiny App learning reasons (dynamically change inputs based on selection)

# Shiny App

## 1. User Inputs

```{r}
# number of people invited
invites <- 150

# total budget
budget <- 30000

# risk tolerance
risk_tolerance <- .20

# inputs for total cost calculation
fixed_cost <- 22000
guest_base <- 50
variable_guest_cost <- 125
```

## 2. Simulation

### 3.2 Run Simulation

```{r}
simulation = py$RiskSimulator(k = 10000, 
                              n = 150, 
                              p = list('left' = .60, 'mode' = .75, 'right' = .90),
                              fixed_cost = 22000, 
                              variable_guest_cost = 125, 
                              guest_base = 50, 
                              budget = 30000,
                              risk_tolerance = 0.2,
                              distribution = 'triangular')

simulation$run()
```

### 3.3 Provide Recommendation

```{r}
simulation$get_recommendation()
```

## 4. Plot Results

### 4.1 Functions

```{r}
# plot.R

# plot guest count distribution with 95% confidence interval
plot_guest_count <- function(simulation_tbl) {
  
  # generate 2.5 and 97.5 percentiles from simulation data
  ci_int_guest <- quantile(simulation_tbl$total_guests, p = c(0.025, .975))
  
  # create histogram plot of results
  p <- simulation_tbl %>%
    ggplot(aes(total_guests)) +
    geom_histogram(binwidth = 1, 
                   fill = cb_palette[6],
                   color = "white") +
    geom_hline(yintercept = 0, size = .5, colour="#333333") +
    geom_vline(xintercept = ci_int_guest[1], linetype = "dashed") +
    geom_vline(xintercept = ci_int_guest[2], linetype = "dashed") +
    labs(title = "Total Guest Count",
         subtitle = str_glue("95% Confidence Estimate: {ci_int_guest[1]} -",
                         "{ci_int_guest[2]} guests"),
         x = "Total Guests",
         y = "Simulation Trials",
         caption = "Source: Simulation Results")
  
  return(p) 
}


# plot cost distribution with 95% confidence interval
plot_cost <- function(simulation_tbl, variable_guest_cost = 125) {
  
  ci_int_cost <- quantile(simulation_tbl$total_cost, p = c(0.025, .975))

  # create histogram of results
  p <- simulation_tbl %>%
    ggplot(aes(total_cost)) +
    # histogram bin size should be equal to per guest variable cost
    geom_histogram(binwidth = variable_guest_cost,
                   fill = cb_palette[8],
                   color = "white") +
    geom_hline(yintercept = 0, size = .5, colour="#333333") +
    labs(title = "Total Guest Cost",
         subtitle = str_glue("95% Confidence Estimate: ${ci_int_cost[1]} -",
                         "${ci_int_cost[2]}"),
         x = "Total Cost",
         y = "Simulation Trials",
         caption = "Source: Simulation Results") +
    geom_vline(xintercept = ci_int_cost[1], linetype = "dashed") +
    geom_vline(xintercept = ci_int_cost[2], linetype = "dashed")
  
  return(p)
}


# plot the risk profile with probability of going over budget
plot_risk <- function(simulation_tbl, variable_guest_cost = 125) {
  
  simulation_tbl$over_budget <- 
    factor(simulation_tbl$over_budget, levels = c("No", "Even", "Yes"))
  
  ci_int_risk <- quantile(simulation_tbl$risk, p = c(0.025, .975))
  
  # risk profile
  p_over_budget <- simulation_tbl %>%
    summarise(p_val = mean(risk < 0))
  
  # plot risk profile with 95% confidence interval
  p <- simulation_tbl %>%
    # color histrogram bins based on positive/negative risk
    ggplot(aes(risk, fill = over_budget)) +
    # histogram bin size should be equal to per guest variable cost
    geom_histogram(binwidth = variable_guest_cost,
                   color = "white") +
    geom_hline(yintercept = 0, size = .5, colour = "#333333") +
    scale_fill_manual(values = c(cb_palette[4], cb_palette[5], cb_palette[7])) +
    labs(title = "Total Budget Risk",
         subtitle = str_glue("95% Confidence Estimate: ${ci_int_risk[1]} -",
                             "${ci_int_risk[2]} ",
                             "({p_over_budget * 100}% risk)"),
         x = "",
         y = "Simulation Trials",
         caption = "Source: Simulation Results") +
    guides(fill = FALSE) +
    geom_vline(xintercept = ci_int_risk[1], linetype = "dashed") +
    geom_vline(xintercept = ci_int_risk[2], linetype = "dashed")
  
    # if there are no even budget outcomes
  if (length(unique(simulation_tbl$over_budget)) < 3) {
    p <- p +
      scale_fill_manual(values = c(cb_palette[4], cb_palette[7]))
  }
  
  return(p)
}

# plot the distribution of recommendation outcomes
plot_recommendation <- function(simulation_obj) {
  
  # get recommendation for subtitle
  simulation_tbl <- simulation_obj$simulation_data
  ovr_recommendation <- simulation_obj$recommendation

  # build main plot
  p <- simulation_tbl %>%
    ggplot(aes(recommendation, fill = recommendation)) +
    # convert counts to percentages
    geom_bar(aes(y = (..count..) / sum(..count..))) + 
    scale_y_continuous(labels = function(x) str_glue("{round(x * 100, 2)}%")) +
    labs(
      title = "Recommendation Outcomes",
      subtitle = str_glue("Overall Recommendation: {ovr_recommendation}"),
      x = "",
      y = "Simulation Trials",
      caption = "Source: Simulation Results"
    ) +
    guides(fill = FALSE) +
    geom_hline(yintercept = 0, size = .5, colour = "#333333") +
    # add dashed line for risk tolernace
    geom_hline(yintercept = risk_tolerance, linetype = "dashed")
  
  # if risk tolerance is exceeded, color the Invite Less bar 
  if (mean(simulation_tbl$risk < 0) >= risk_tolerance) {
    p <- p + 
    scale_fill_manual(values = c(cb_palette[1], cb_palette[7]))
  } else {
  # else color the Invite All bar
    p <- p + 
    scale_fill_manual(values = c(cb_palette[4], cb_palette[1]))
  }
  
  return(p)
}
```

### 4.2 Plot Guest Count

```{r}
plot_guest_count(simulation$simulation_data)
```

### 4.3 Plot Cost

```{r}
plot_cost(simulation$simulation_data)
```

### 4.4 Plot Risk

```{r}
plot_risk(simulation$simulation_data)
```

### 4.5 Plot Recommendation

```{r}
plot_recommendation(simulation)
```

## 5. Financial Outcomes

### 5.1 Upside Potential

```{r}
simulation$financial_upside
```

### 5.2 Downside Risk

```{r}
simulation$financial_risk
```

### 5.3 Overall Expectation

```{r}
simulation$overall_expectation
```

